Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
update sec. 2

\textbf{Function space} \todo{Could be titled some other way, like Function-space representation}
%As a neural network is a deterministic mapping, the weight-space posterior induces a distribution over the function values.
%Intuitively, if one was to sample from the weight posterior, the corresponding functions created can
%be viewed as perturbed versions of the function at the MAP estimate $f_{\vw^*}$.
%In most applications, we care about predictions from the neural network and not the weights themselves.
%As such, it is the distribution over function values that we are actually interested in.
While neural networks are deterministic mappings defined by their weights, the ultimate goal of training a neural network is to optimize the function it represents, not the weights themselves. Consequently, the weight-space posterior corresponds to a distribution over function values. Imagine sampling from the weight posterior; the resulting functions could be viewed as perturbations of the function at the MAP estimate $f_{\vw^*}$. This perspective aligns better with the main objective in most applications: making representative predictions given the observations we have.

>>>>

\textbf{Neural Network Function-space} %\todo{Could be titled some other way, like Function-space representation}
%As a neural network is a deterministic mapping, the weight-space posterior induces a distribution over the function values.
%Intuitively, if one was to sample from the weight posterior, the corresponding functions created can
%be viewed as perturbed versions of the function at the MAP estimate $f_{\vw^*}$.
%In most applications, we care about predictions from the neural network and not the weights themselves.
%As such, it is the distribution over function values that we are actually interested in.
Neural networks are deterministic parametric functions, but even if the training is typically an optimization in the weight-space, in most applications, we are interested in the parametrized function and not in the weights themselves.
%While neural networks are deterministic mappings defined by their weights, the ultimate goal of training a neural network is to optimize the function it represents, not the weights themselves. 
Consequently, the weight-space posterior corresponds to a distribution over function values. 
Intuitively, if one was to sample from the weight posterior, the corresponding functions created can be viewed as perturbed versions of the function at the MAP estimate $f_{\vw^*}$. This perspective aligns better with the main objective of making representative predictions given the observations.
